Import_Map

### 2024-06-09 Code/Plots_ProNicheMap.Rmd
Regenerated a larger Niches figure and saved to .tiff

FigPath <- file.path("..", "Output", "Figures")
```

```{r read photoperiod depth data}
PhotoperiodDepth <- readRDS(file = file.path("..", "Data", "ProcessedData", "DepthPhotoperiodTableFilter.Rds"))

PhotoperiodDepthOMZ <- PhotoperiodDepth |>
  select(-c(ToD, DepthPARabs, DepthPARSine, DepthPARabsNA, Photicperiod:PhoticperiodSineSatPAR_h)) |>
  filter(DepthNames %in% c("50 m", "100 m")) |>
  mutate(DepthNames = factor(DepthNames, levels = c("100 m", "50 m")),
         lat = factor(lat, levels = c("45", "0"))) |>
  relocate(DepthNames, .after = lat) |>
  mutate(CladeHLI = case_when(DayofYear == "Winter Solstice" & lat == 45 ~ 0,
                              DayofYear == "Equinox" & DepthNames == "100 m" & lat == 45 ~ 0,
                              DayofYear == "Summer Solstice" & DepthNames == "100 m" & lat == 0  ~ 0,
                              TRUE ~ 1)) |>
  mutate(CladeLLII_LLIII = case_when(DayofYear == "Winter Solstice" & DepthNames == "100 m" & lat == 45 ~ 0,
                                     DayofYear == "Winter Solstice" & DepthNames == "50 m" & lat == 0 ~ 0,
                                     DayofYear == "Equinox" & DepthNames == "50 m" ~ 0,
                                     DayofYear == "Summer Solstice" & lat == 45  ~ 0,
                                     DayofYear == "Summer Solstice" & DepthNames == "50 m" & lat == 0  ~ 0,
                              TRUE ~ 1 ))  |>
  mutate(CladeLLIV = case_when(DayofYear == "Winter Solstice" & DepthNames == "100 m" & lat == 45 ~ 0,
                              TRUE ~ 1))

@@

library("png")
DepthBackdrop <- readPNG("DepthBackdrop.png")
# Get dimensions of the image
width <- dim(DepthBackdrop)[2]
height <- dim(DepthBackdrop)[1]

# Plot the image
plot(1:width, type = "n", xlim = c(0, width), ylim = c(0, height),
     xlab = "", ylab = "", axes =FALSE)
rasterImage(DepthBackdrop, 0, 0, width, height) 
points(PhotoperiodDepthFullO2$PhoticperiodPeakSatPAR_h, PhotoperiodDepthFullO2$DepthNames, col = "red", pch = 16)

```
#fig.height = 10, fig.width = 8, warning = FALSE
```{r, Niches figures}
NichesFullO2North <- PhotoperiodDepthFullO2 %>%
  filter(lat == 45) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 5) %>% 
mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
         lat = factor(lat, levels = c("45", "0"))) %>%
ggplot()+
  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
            size = 0.5, alpha = 0, show.legend = TRUE)+
  labs(title = "Full Oxygen") +
  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
    facet_grid(rows = vars(lat),
              cols = vars(DayofYear),
              labeller = labeller(lat = label_both, DayofYear = label_both)) +
   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
   # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 3
  )  +
  guides(color = "none") +
  theme_bw()+
 theme(strip.text = element_text(size = 10),
        axis.title = element_blank(),
        # strip.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 10),
        axis.text.x = element_blank(),
        axis.ticks.x.bottom = element_blank(),
        axis.ticks.y.left = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        plot.margin = unit(c(0,30,0,0), "pt"))

NichesFullO2North

NichesFullO2Equat <- PhotoperiodDepthFullO2 %>%
  filter(lat == 0) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 5) %>% 
mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
         lat = factor(lat, levels = c("45", "0"))) %>%
ggplot()+
  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
            size = 0.5, alpha = 0, show.legend = TRUE)+
  # labs(title = "Full Oxygen") +
  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
    facet_grid(rows = vars(lat),
              cols = vars(DayofYear),
              labeller = labeller(lat = label_both)) +
   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
   # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 3
  )  +
  guides(color = "none") +
  theme_bw() +
 theme(strip.text.x = element_blank(),
       strip.text.y = element_text(size = 10),
        axis.title = element_blank(),
        # strip.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 10),
        # axis.text.y = element_blank(),
        # axis.text.y = element_text(size = 5),
         axis.text.x = element_blank(),
        axis.ticks.x.bottom = element_blank(),
        axis.ticks.y.left = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank())

NichesOMZNorth <- PhotoperiodDepthOMZ %>%
  filter(lat == 45) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 5) %>% 
mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
         lat = factor(lat, levels = c("45", "0"))) %>%
ggplot()+
  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
            size = 0.5, alpha = 0, show.legend = TRUE)+
   labs(title = "OMZ") +
  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
    facet_grid(rows = vars(lat),
              cols = vars(DayofYear),
              labeller = labeller(lat = label_both)) +
   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
   # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 3
  )  +
  guides(color = "none") +
  theme_bw() +
 theme(strip.text.x = element_text(size = 10),
       strip.text.y = element_text(size = 10),
        axis.title = element_blank(),
        # strip.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 10),
        # axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x.bottom = element_blank(),
        axis.ticks.y.left = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank())

NichesOMZEquat <- PhotoperiodDepthOMZ %>%
  filter(lat == 0) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 5) %>% 
mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
         lat = factor(lat, levels = c("45", "0"))) %>%
ggplot()+
  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
            size = 0.5, alpha = 0, show.legend = TRUE)+
  # labs(title = "Full Oxygen") +
  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
    facet_grid(rows = vars(lat),
              cols = vars(DayofYear),
              labeller = labeller(lat = label_both)) +
   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
   # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 3
  )  +
  guides(color = "none") +
  theme_bw() +
 theme(strip.text.x = element_blank(),
       strip.text.y = element_text(size = 10),
        axis.title = element_blank(),
        # strip.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 10),
        # axis.text.y = element_blank(),
         axis.text.x = element_blank(),
        axis.ticks.x.bottom = element_blank(),
        axis.ticks.y.left = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank())

@@

d=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(35), y2=c(55))
d2=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-35), y2=c(-55))
d3=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-Inf), y2=c(Inf))
d4=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-15), y2=c(15))
d5=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-40), y2=c(40))
# 
# data_textTropicFull <- data.frame(label = c('All~year'))
# data_textTropicFull2 <- data.frame(label = c('12~h'))
# data_textTropicFull3 <- data.frame(label = c('11/7~h'))
# 
# TropicFull<-ggplot() + 
#   geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
#   geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
#   geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
#   geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
#   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
#   geom_text(data=data_textA, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
#   geom_text(data=data_textTropicFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
#   geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
#   geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
#   scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
#   coord_cartesian(ylim = c(-90, 120)) +
#   labs(y = "Latitude", x = "Longitude") +
#   ggh4x::facet_nested(rows = vars(facetsPresent), labeller = label_parsed, switch = "y") +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank(),
#         panel.grid.major = element_blank(),
#         strip.placement = "outside",
#         strip.switch.pad.grid = unit(1, "cm"),
#         axis.text = element_text(size=14),
#         axis.title = element_text(size=14),
#         strip.background = element_rect(fill="white"),
#         strip.text = element_text(size=18),
#         axis.title.y = element_text(vjust = -15),
#         #axis.title.x = element_text(margin=margin(t=10)),
#         axis.title.x = element_blank(),
#         axis.text.x = element_blank(),
#         axis.ticks.x = element_blank(),
#         legend.background = element_rect(fill="transparent"),
#         legend.position = c(0.12,0.76),
#         legend.key.height= unit(0.005, 'cm'),
#         legend.spacing.x = unit(0.01, 'cm'),
#         legend.text = element_text(size=14))
# TropicFull

# data_textWinterFull <- data.frame(label = c('Winter~or~summer~solstice'))
# data_textWinterFull2 <- data.frame(label = c('9~h'))
# data_textWinterFull3 <- data.frame(label = c('16~h'))
# data_textWinterFull4 <- data.frame(label = c('8/4~h'))
# data_textWinterFull5 <- data.frame(label = c('15/10~h'))

>>>>

PlotsOut <- file.path("..","Output", "Figures")
PlotsOutPLOS <- file.path("..", "OutPut", "PLOSRound2")
```

```{r read photoperiod depth data}

PhotoperiodDepth <- readRDS(file = file.path("..", "Data", "ProcessedData", "DepthPhotoperiodTableFilter.Rds"))

```{r create df for full oxygen and OMZ potential niches}

# add column for each clade with 1 for potential and 0 for no potential niche based on PAR at corresponding depths (50 and 100 m)   for temporal and equatorial zones.
PhotoperiodDepthOMZ <- PhotoperiodDepth |>
  select(-c(ToD, DepthPARabs, DepthPARSine, DepthPARabsNA, Photicperiod:PhoticperiodSineSatPAR_h)) |>
  filter(DepthNames %in% c("50 m", "100 m")) |>
  mutate(DepthNames = factor(DepthNames, levels = c("100 m", "50 m")),
         lat = factor(lat, levels = c("45", "0"))) |>
  relocate(DepthNames, .after = lat) |>
  mutate(CladeHLI = case_when(DayofYear == "Winter Solstice" & lat == 45 ~ 0,
                              DayofYear == "Equinox" & DepthNames == "100 m" & lat == 45 ~ 0,
                              DayofYear == "Summer Solstice" & DepthNames == "100 m" & lat == 0  ~ 0,
                              TRUE ~ 1)) |>
  mutate(CladeLLII_LLIII = case_when(DayofYear == "Winter Solstice" & DepthNames == "100 m" & lat == 45 ~ 0,
                                     DayofYear == "Winter Solstice" & DepthNames == "50 m" & lat == 0 ~ 0,
                                     DayofYear == "Equinox" & DepthNames == "50 m" ~ 0,
                                     DayofYear == "Summer Solstice" & lat == 45  ~ 0,
                                     DayofYear == "Summer Solstice" & DepthNames == "50 m" & lat == 0  ~ 0,
                              TRUE ~ 1 ))  |>
  mutate(CladeLLIV = case_when(DayofYear == "Winter Solstice" & DepthNames == "100 m" & lat == 45 ~ 0,
                              TRUE ~ 1))

@@

# library("png")
# DepthBackdrop <- readPNG("DepthBackdrop.png")
# # Get dimensions of the image
# width <- dim(DepthBackdrop)[2]
# height <- dim(DepthBackdrop)[1]
# 
# # Plot the image
# plot(1:width, type = "n", xlim = c(0, width), ylim = c(0, height),
#      xlab = "", ylab = "", axes =FALSE)
# rasterImage(DepthBackdrop, 0, 0, width, height) 
# points(PhotoperiodDepthFullO2$PhoticperiodPeakSatPAR_h, PhotoperiodDepthFullO2$DepthNames, col = "red", pch = 16)

#fig.height = 10, fig.width = 8, warning = FALSE
```{r, Niches figures}
# 
# 
# NichesFullO2North <- PhotoperiodDepthFullO2 %>%
#   filter(lat == 45) %>% 
# mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
#                                 CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
#                                 CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
#                                 CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
#                                 CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
#                                 CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
#                                 CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
#                                 CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
#         TextLocation = 5) %>% 
# mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
#          lat = factor(lat, levels = c("45", "0"))) %>%
# ggplot()+
#   geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
#             size = 0.5, alpha = 0, show.legend = TRUE)+
#   labs(title = "Full Oxygen") +
#   scale_x_continuous(breaks=seq(0, 25, by = 5)) +
#     facet_grid(rows = vars(lat),
#               cols = vars(DayofYear),
#               labeller = labeller(lat = label_both, DayofYear = label_both)) +
#    geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
#    # parse = TRUE,
#     hjust = 0,
#     vjust = 1,
#     size = 3
#   )  +
#   guides(color = "none") +
#   theme_bw()+
#  theme(strip.text = element_text(size = 10),
#         axis.title = element_blank(),
#         # strip.text.x = element_text(size = 20),
#         axis.text.y = element_text(size = 10),
#         axis.text.x = element_blank(),
#         axis.ticks.x.bottom = element_blank(),
#         axis.ticks.y.left = element_blank(),
#         panel.grid.minor = element_blank(),
#         panel.grid.major = element_blank(),
#         plot.margin = unit(c(0,30,0,0), "pt"))
# 
# NichesFullO2North
# 
# NichesFullO2Equat <- PhotoperiodDepthFullO2 %>%
#   filter(lat == 0) %>% 
# mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
#                                 CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
#                                 CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
#                                 CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
#                                 CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
#                                 CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
#                                 CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
#                                 CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
#         TextLocation = 5) %>% 
# mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
#          lat = factor(lat, levels = c("45", "0"))) %>%
# ggplot()+
#   geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
#             size = 0.5, alpha = 0, show.legend = TRUE)+
#   # labs(title = "Full Oxygen") +
#   scale_x_continuous(breaks=seq(0, 25, by = 5)) +
#     facet_grid(rows = vars(lat),
#               cols = vars(DayofYear),
#               labeller = labeller(lat = label_both)) +
#    geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
#    # parse = TRUE,
#     hjust = 0,
#     vjust = 1,
#     size = 3
#   )  +
#   guides(color = "none") +
#   theme_bw() +
#  theme(strip.text.x = element_blank(),
#        strip.text.y = element_text(size = 10),
#         axis.title = element_blank(),
#         # strip.text.x = element_text(size = 20),
#         axis.text.y = element_text(size = 10),
#         # axis.text.y = element_blank(),
#         # axis.text.y = element_text(size = 5),
#          axis.text.x = element_blank(),
#         axis.ticks.x.bottom = element_blank(),
#         axis.ticks.y.left = element_blank(),
#         panel.grid.minor = element_blank(),
#         panel.grid.major = element_blank())
# 
# NichesFullO2Equat
# 
# 
# NichesOMZNorth <- PhotoperiodDepthOMZ %>%
#   filter(lat == 45) %>% 
# mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
#                                 CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
#                                 CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
#                                 CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
#                                 CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
#                                 CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
#                                 CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
#                                 CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
#         TextLocation = 5) %>% 
# mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
#          lat = factor(lat, levels = c("45", "0"))) %>%
# ggplot()+
#   geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
#             size = 0.5, alpha = 0, show.legend = TRUE)+
#    labs(title = "OMZ") +
#   scale_x_continuous(breaks=seq(0, 25, by = 5)) +
#     facet_grid(rows = vars(lat),
#               cols = vars(DayofYear),
#               labeller = labeller(lat = label_both)) +
#    geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
#    # parse = TRUE,
#     hjust = 0,
#     vjust = 1,
#     size = 3
#   )  +
#   guides(color = "none") +
#   theme_bw() +
#  theme(strip.text.x = element_text(size = 10),
#        strip.text.y = element_text(size = 10),
#         axis.title = element_blank(),
#         # strip.text.x = element_text(size = 20),
#         axis.text.y = element_text(size = 10),
#         # axis.text.y = element_blank(),
#         axis.text.x = element_blank(),
#         axis.ticks.x.bottom = element_blank(),
#         axis.ticks.y.left = element_blank(),
#         panel.grid.minor = element_blank(),
#         panel.grid.major = element_blank())
# 
# NichesOMZNorth
# 
# 
# 
# 
# NichesOMZEquat <- PhotoperiodDepthOMZ %>%
#   filter(lat == 0) %>% 
# mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
#                                 CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
#                                 CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
#                                 CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
#                                 CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
#                                 CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
#                                 CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
#                                 CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
#         TextLocation = 5) %>% 
# mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
#          lat = factor(lat, levels = c("45", "0"))) %>%
# ggplot()+
#   geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
#             size = 0.5, alpha = 0, show.legend = TRUE)+
#   # labs(title = "Full Oxygen") +
#   scale_x_continuous(breaks=seq(0, 25, by = 5)) +
#     facet_grid(rows = vars(lat),
#               cols = vars(DayofYear),
#               labeller = labeller(lat = label_both)) +
#    geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
#    # parse = TRUE,
#     hjust = 0,
#     vjust = 1,
#     size = 3
#   )  +
#   guides(color = "none") +
#   theme_bw() +
#  theme(strip.text.x = element_blank(),
#        strip.text.y = element_text(size = 10),
#         axis.title = element_blank(),
#         # strip.text.x = element_text(size = 20),
#         axis.text.y = element_text(size = 10),
#         # axis.text.y = element_blank(),
#          axis.text.x = element_blank(),
#         axis.ticks.x.bottom = element_blank(),
#         axis.ticks.y.left = element_blank(),
#         panel.grid.minor = element_blank(),
#         panel.grid.major = element_blank())
# 
# NichesOMZEquat

@@

FullO2map<-ggplot() + 
  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
    geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
  geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
    geom_text(data=data_textA, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
  coord_cartesian(ylim = c(-90, 120)) +
  labs(y = "Latitude", x = "Longitude") +
  # ggh4x::facet_nested(rows = vars(facetsFuture), labeller = label_parsed, switch = "y") +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        strip.placement = "outside",
        strip.switch.pad.grid = unit(1, "cm"),
        axis.text = element_text(size=14),
        axis.title = element_text(size=14),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=18),
        axis.title.y = element_text(vjust = 1),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
FullO2map

OMZmap<-ggplot() + 
  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
  geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
     geom_text(data=data_textB, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
  coord_cartesian(ylim = c(-90, 120)) +
  labs(y = "Latitude", x = "Longitude") +
  # ggh4x::facet_nested(rows = vars(facetsFuture), labeller = label_parsed, switch = "y") +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        strip.placement = "outside",
        strip.switch.pad.grid = unit(1, "cm"),
        axis.text = element_text(size=14),
        axis.title = element_text(size=14),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=18),
        axis.title.y = element_text(vjust = 1),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
OMZmap
